Toward \earlywarning\ detection of gravitational waves from compact binary coalescence

### 2011-07-04 method.tex
Spelled out 'seconds' where it was not clear whether 's' was a symbol in an expression or a unit
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1237 ccdd05d5-56c1-461a-bf98-85f6876523b4
More descriptive title for section 3
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1250 ccdd05d5-56c1-461a-bf98-85f6876523b4

\section{A novel near real-time algorithm}
\label{sec:method}

@@

First, the sample rate of the detector data must be decimated to match sample rates
with each of the time slices.  We will denote the decimated detector data streams using
a superscript $^s$ to indicate the time slices to which they correspond, and the
operator $H^\shortdownarrow$ will represent the appropriate decimation filter:
\begin{equation*}
\label{eq:decomp}
	x^{s+1}[k] = \left( H^\shortdownarrow x^s\right)[k].
\end{equation*}
We shall use the symbol $H^\shortuparrow$ to represent an interpolation filter,
\begin{equation*}
	x^{s}[k] = \left( H^\shortuparrow x^{s+1}\right)[k].
\end{equation*}
Ultimately, the latency of the entire \lloid\ algorithm is set by the decimation
and interpolation filters because they are generally time-symmetric.  As a result,
\lloid\ is very slightly acausal with an intrinsic latency of
$\left(\max \left( N^\shortdownarrow, N^\shortuparrow \right) / 2 f^0 \right)$~s.

>>>>

\section{Novel near real-time algorithm for \CBC\ detection}
\label{sec:method}

@@

First, the sample rate of the detector data must be decimated to match sample rates
with each of the time slices.  We will denote the decimated detector data streams using
a superscript $^s$ to indicate the time slices to which they correspond, and the
operator $H^\shortdownarrow$ will represent the appropriate decimation filter:
\begin{equation*}
\label{eq:decomp}
	x^{s+1}[k] = \left( H^\shortdownarrow x^s\right)[k].
\end{equation*}
We shall use the symbol $H^\shortuparrow$ to represent an interpolation filter,
\begin{equation*}
	x^{s}[k] = \left( H^\shortuparrow x^{s+1}\right)[k].
\end{equation*}
Ultimately, the latency of the entire \lloid\ algorithm is set by the decimation
and interpolation filters because they are generally time-symmetric.  As a result,
\lloid\ is very slightly acausal with an intrinsic latency of
$\left(\max \left( N^\shortdownarrow, N^\shortuparrow \right) / 2 f^0 \right)$~seconds.
